Boolean Operations for Surfaces in VTK Without External Libraries

### 2011-05-11 Document/LaTeX/Article.tex
Converging to a final draft.

@@

XXXX Change this in the source code documentation.

@@

$\downarrow$

\code{vtkPolyDataDistance}

@@

\code{vtkThreshold} \hspace{1em} \code{vtkThreshold}

$\downarrow$ \hspace{6em}  $\downarrow$

\code{vtkDataSetSurfaceFilter} \hspace{1em} \code{vtkDataSetSurfaceFilter}

@@

%\input{ResultsFigure.tex}

>>>>

\section{Previous Work}

Lloyd previously contributed a VTK class for computing boolean operations on surface meshes. His contribution wrapped the GNU Triangulated Surface Library (GTS) in a VTK class that performed conversion between the VTK mesh data structure and the GTS mesh data structure and vice versa. This work filled a need often requested by users on the VTK mailing lists.

Unfortunately, his work is unable to be incorporated into the main VTK repository because of the  incompatible GTS license. Furthermore, any projects using Lloyd's contribution are subject to the licensing requirements of GTS. Our contribution is not subject to an incompatible license as it makes use of no external libraries or code.

Furthermore, our contribution copies point and cell data from the input meshes to the output meshes appropriately, interpolating point data where necessary. When portions of two input meshes are combined into one mesh, only the common point and cell data in both meshes is copied to the output.

@@

@@

@@

\code{vtkImplicitPolyData} $\rightarrow$ \code{vtkClipPolyData} \hspace{1em} \code{vtkClipPolyData} $\leftarrow$ \code {vtkImplicityPolyData}

@@

\input{ResultsFigure.tex}
